---
title: "Everyday LA: Research Methods (Spring 2017)"
output: 
  flexdashboard::flex_dashboard
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(gsheet)
library(tidyr)
suppressMessages(library(dplyr))
library(data.table)
library(rvest)
library(ggplot2)
library(ineq)
library(syuzhet)
library(tm)
library(wordcloud)
library(SnowballC)
library(stringi)
library(stringr)
library(scales)


URL_Exp_Block1 <- 'https://docs.google.com/spreadsheets/d/1j1S60E64E0voiGaBbF3qFhM6H2QPJOBhUQPlhT0CO-A/edit?usp=sharing'
URL_Exp_Block2 <- 'https://docs.google.com/spreadsheets/d/15wmGjILdk0NT2ELa3lD5SfHyudNELhTIxJ5OpP8n1Uc/edit?usp=sharing'
URL_Exp_Block3 <- 'https://docs.google.com/spreadsheets/d/1wTQwxhG6knUH8B5neJ_Du3sNCr2GRQ_ie376QVWU4IE/edit?usp=sharing'
URL_Exp_Block4 <- 'https://docs.google.com/spreadsheets/d/1AAuOnhI6nIImODoz-LSpzr72idbFlZUuFYkOX7Y27xM/edit?usp=sharing'



# Define the data gathering function here? possibly using
# http://shiny.rstudio.com/reference/shiny/latest/reactivePoll.html
# http://shiny.rstudio.com/gallery/reactive-poll-and-file-reader.html

pollSpreadsheet <- function(url, namesCol=NULL, factors=NULL){
  data <- reactivePoll(5000, session,
                     readLastTimestamp <- function(){
                        # We read the latest response timestamp
                        data <- as.data.frame(gsheet2tbl(url))
                        if(nrow(data)>0 & ncol(data)>1){
                          data[nrow(data),1]
                        }else{
                          ""
                        }
                      },
                     readValue <- function(){
                        data <- as.data.frame(gsheet2tbl(url))
                        #We clean it up a bit
                        if(!is.null(namesCol) & length(namesCol)>0){
                          names(data) <- namesCol 
                        }
                        if(!is.null(factors) & length(factors)>0){
                          for(f in factors){
                            data[,f] <- as.factor(data[,f])
                          }  
                        }
                        data
                      })
  data
}


expBlock1Data <- pollSpreadsheet(URL_Exp_Block1, 
                          c("Timestamp","Name1","Name2","Treatment","Manipulation.Check","Independent","Dependent"),
                          c("Name1","Name2"))

expB1D <- reactive({
  data <- expBlock1Data()
  data
})

expBlock2Data <- pollSpreadsheet(URL_Exp_Block2, 
                          c("Timestamp","Name1","Name2","Design","Quasi"),
                          c("Name1","Name2","Design"))

expB2D <- reactive({
  data <- expBlock2Data()
  data
})


expBlock3Data <- pollSpreadsheet(URL_Exp_Block3, 
                          c("Timestamp","Name1","Name2","Control","Internal.Validity"),
                          c("Name1","Name2"))

expB3D <- reactive({
  data <- expBlock3Data()
  data
})

expBlock4Data <- pollSpreadsheet(URL_Exp_Block4, 
                          c("Timestamp","Name1","Name2","Company.Research","Benefits","Conflict"),
                          c("Name1","Name2"))

expB4D <- reactive({
  data <- expBlock4Data()
  data
})



convertFactor <- function(values){
  print(values)
  if(!is.null(values) & length(values)>0){
    newvals = numeric()
    for(val in values){
      if(grepl(as.character(val),"Strongly agree",fixed = T)){
        newval = 5
      }else if(grepl(as.character(val),"Agree",fixed = T)){
        newval = 4
      }else if(grepl(as.character(val),"Neither agree nor disagree",fixed = T)){
        newval = 3
      }else if(grepl(as.character(val),"Disagree",fixed = T)){
        newval = 2
      }else if(grepl(as.character(val),"Strongly disagree",fixed = T)){
        newval = 1
      }else if(grepl(as.character(val),"Not Applicable",fixed = T)){
        newval = NA
      }
      newvals <- c(newvals, newval)
    }
    print(newvals)
    newvals
  }else{
    values
  }
}



      count_words <- function(s){
        #count <- as.numeric(stri_stats_latex(s)['Words'])
        count <- vapply(strsplit(s, "\\W+"), length, integer(1))
        count
      }

  clean_vector <- function(v){
    newv <- v[v!=""]
    newv2 <- newv[nchar(newv)>1]
    newv2
  }
      
integer_breaks <- function(x)
  seq(floor(min(x)), ceiling(max(x)))

#sessions <- read.csv(file = "Sessions.csv", encoding="UTF-8", stringsAsFactors=FALSE)

```


Block 1
=====================================  

Column 1 
-------------------------------------

### What was the treatment: WordCloud

```{r}

renderPlot({
   data <- expB1D()
    treat <- data[,"Treatment"]
    if(length(treat)>0){
      d <- unlist(string.break.line(paste(treat,sep="\n")))
      d <- clean_vector(d)
      if(length(d)>0){
        corpus <- Corpus(VectorSource(d))
        corpus <- tm_map(corpus, removePunctuation)
        corpus <- tm_map(corpus, tolower)
        corpus <- tm_map(corpus, removeWords, stopwords("english"))
        corpus <- tm_map(corpus, stemDocument)
        corpus <- tm_map(corpus, PlainTextDocument)
        wordcloud(corpus, max.words=100, random.order=F)
      }  
    }
})
```


### What was the treatment: Responses


```{r}

library(Hmisc)

renderTable({
 data <- expB1D()
 treat <- data[,"Treatment"]
 if(length(treat)>0){
  resp <- unlist(string.break.line(treat))
 }else{
   resp <- c("")
 }
 resp <- clean_vector(resp)
 data.frame(Response=resp)
 
})


```


Column 2 
-------------------------------------

### Manipulation Check: WordCloud


```{r}

renderPlot({
   data <- expB1D()
    mc <- data[,"Manipulation.Check"]
    if(length(mc)>0){
      d <- unlist(string.break.line(paste(mc,sep="\n")))
      d <- clean_vector(d)
      if(length(d)>0){
        corpus <- Corpus(VectorSource(d))
        corpus <- tm_map(corpus, removePunctuation)
        corpus <- tm_map(corpus, tolower)
        corpus <- tm_map(corpus, removeWords, stopwords("english"))
        corpus <- tm_map(corpus, stemDocument)
        corpus <- tm_map(corpus, PlainTextDocument)
        wordcloud(corpus, max.words=100, random.order=F)
      }  
    }
})
```




### Manipulation check: Responses


```{r}

library(Hmisc)

renderTable({
 data <- expB1D()
 mc <- data[,"Manipulation.Check"]
 if(length(mc)>0){
  resp <- unlist(string.break.line(mc))
 }else{
   resp <- c("")
 }
 resp <- clean_vector(resp)
 data.frame(Response=resp)
 
})


```

Column 3
-------------------------------------

### Independent variables


```{r}

renderPlot({
   data <- expB1D()
    ind <- data[,"Independent"]
    if(length(ind)>0){
      df <- data.frame(Responses=as.factor(unlist(strsplit(ind, split=", ", fixed = T))))
      if(nrow(df)>0){
        ggplot(df, aes(x=Responses, fill=Responses)) +
  geom_bar(stat="count") +
  scale_y_continuous(breaks=integer_breaks) +
  coord_flip() + guides(fill=FALSE) +
  theme_bw() + scale_fill_brewer(palette="Set1") + theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))
      }  
    }
})
```

### Dependent variables


```{r}

renderPlot({
   data <- expB1D()
    ind <- data[,"Dependent"]
    if(length(ind)>0){
      df <- data.frame(Responses=as.factor(unlist(strsplit(ind, split=", ", fixed = T))))
      if(nrow(df)>0){
        ggplot(df, aes(x=Responses, fill=Responses)) +
  geom_bar(stat="count") +
  scale_y_continuous(breaks=integer_breaks) +
  coord_flip() + guides(fill=FALSE) +
  theme_bw() + scale_fill_brewer(palette="Set1") + theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))
      }  
    }
})
```





Block 2
=====================================  

Column 1
-------------------------------------

### Experimental Design


```{r}

renderPlot({
   data <- expB2D()
    ind <- data[,"Design"]
    if(length(ind)>0){
      df <- data.frame(Responses=as.factor(ind))
      if(nrow(df)>0){
        
        levels(df$Responses) <- gsub(" ", "\n", levels(df$Responses))
        ggplot(df, aes(x=Responses, fill=Responses)) +
  geom_bar(stat="count") +
  scale_y_continuous(breaks=integer_breaks) +
  guides(fill=FALSE) +
  theme_bw() + scale_fill_brewer(palette="Set1") + theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))
      }  
    }
})
```


Column 2
-------------------------------------

### Why is this a quasi experiment? What changes to make it experimental? (wordcloud)

```{r}

renderPlot({
   data <- expB2D()
    q <- data[,"Quasi"]
    if(length(q)>0){
      d <- unlist(string.break.line(paste(q,sep="\n")))
      d <- clean_vector(d)
      if(length(d)>0){
        corpus <- Corpus(VectorSource(d))
        corpus <- tm_map(corpus, removePunctuation)
        corpus <- tm_map(corpus, tolower)
        corpus <- tm_map(corpus, removeWords, stopwords("english"))
        corpus <- tm_map(corpus, stemDocument)
        corpus <- tm_map(corpus, PlainTextDocument)
        wordcloud(corpus, max.words=100, random.order=F)
      }  
    }
})
```


### Why is this a quasi experiment? What changes to make it experimental? (responses)


```{r}

library(Hmisc)

renderTable({
 data <- expB2D()
 q <- data[,"Quasi"]
 if(length(q)>0){
  resp <- unlist(string.break.line(q))
 }else{
   resp <- c("")
 }
 resp <- clean_vector(resp)
 data.frame(Response=resp)
 
})


```


Block 3
=====================================  

Column 1 
-------------------------------------

### How authors ensured experimental control? (WordCloud)

```{r}

renderPlot({
   data <- expB3D()
    cont <- data[,"Control"]
    if(length(cont)>0){
      d <- unlist(string.break.line(paste(cont,sep="\n")))
      d <- clean_vector(d)
      if(length(d)>0){
        corpus <- Corpus(VectorSource(d))
        corpus <- tm_map(corpus, removePunctuation)
        corpus <- tm_map(corpus, tolower)
        corpus <- tm_map(corpus, removeWords, stopwords("english"))
        corpus <- tm_map(corpus, stemDocument)
        corpus <- tm_map(corpus, PlainTextDocument)
        wordcloud(corpus, max.words=100, random.order=F)
      }  
    }
})
```


### How authors ensured experimental control? (Responses)


```{r}

library(Hmisc)

renderTable({
 data <- expB3D()
 cont <- data[,"Control"]
 if(length(cont)>0){
  resp <- unlist(string.break.line(cont))
 }else{
   resp <- c("")
 }
 resp <- clean_vector(resp)
 data.frame(Response=resp)
 
})


```


Column 2 
-------------------------------------

### What factors threaten internal validity? (WordCloud)


```{r}

renderPlot({
   data <- expB3D()
    iv <- data[,"Internal.Validity"]
    if(length(iv)>0){
      d <- unlist(string.break.line(paste(iv,sep="\n")))
      d <- clean_vector(d)
      if(length(d)>0){
        corpus <- Corpus(VectorSource(d))
        corpus <- tm_map(corpus, removePunctuation)
        corpus <- tm_map(corpus, tolower)
        corpus <- tm_map(corpus, removeWords, stopwords("english"))
        corpus <- tm_map(corpus, stemDocument)
        corpus <- tm_map(corpus, PlainTextDocument)
        wordcloud(corpus, max.words=100, random.order=F)
      }  
    }
})
```




### What factors threaten internal validity? (Responses)


```{r}

library(Hmisc)

renderTable({
 data <- expB3D()
 iv <- data[,"Internal.Validity"]
 if(length(iv)>0){
  resp <- unlist(string.break.line(iv))
 }else{
   resp <- c("")
 }
 resp <- clean_vector(resp)
 data.frame(Response=resp)
 
})


```



Block 4
=====================================  

Column 1 
-------------------------------------



### What was the company project? and the research project? (WordCloud)

```{r}

renderPlot({
   data <- expB4D()
    cr <- data[,"Company.Research"]
    if(length(cr)>0){
      d <- unlist(string.break.line(paste(cr,sep="\n")))
      d <- clean_vector(d)
      if(length(d)>0){
        corpus <- Corpus(VectorSource(d))
        corpus <- tm_map(corpus, removePunctuation)
        corpus <- tm_map(corpus, tolower)
        corpus <- tm_map(corpus, removeWords, stopwords("english"))
        corpus <- tm_map(corpus, stemDocument)
        corpus <- tm_map(corpus, PlainTextDocument)
        wordcloud(corpus, max.words=100, random.order=F)
      }  
    }
})
```


### What was the company project? and the research project? (Responses)


```{r}

library(Hmisc)

renderTable({
 data <- expB4D()
 cr <- data[,"Company.Research"]
 if(length(cr)>0){
  resp <- unlist(string.break.line(cr))
 }else{
   resp <- c("")
 }
 resp <- clean_vector(resp)
 data.frame(Response=resp)
 
})


```


Column 2 
-------------------------------------

### What benefits the company got from supporting the research project? (WordCloud)


```{r}

renderPlot({
   data <- expB4D()
    ben <- data[,"Benefits"]
    if(length(ben)>0){
      d <- unlist(string.break.line(paste(ben,sep="\n")))
      d <- clean_vector(d)
      if(length(d)>0){
        corpus <- Corpus(VectorSource(d))
        corpus <- tm_map(corpus, removePunctuation)
        corpus <- tm_map(corpus, tolower)
        corpus <- tm_map(corpus, removeWords, stopwords("english"))
        corpus <- tm_map(corpus, stemDocument)
        corpus <- tm_map(corpus, PlainTextDocument)
        wordcloud(corpus, max.words=100, random.order=F)
      }  
    }
})
```




### What benefits the company got from supporting the research project? (Responses)


```{r}

library(Hmisc)

renderTable({
 data <- expB4D()
 ben <- data[,"Benefits"]
 if(length(ben)>0){
  resp <- unlist(string.break.line(ben))
 }else{
   resp <- c("")
 }
 resp <- clean_vector(resp)
 data.frame(Response=resp)
 
})


```


Column 3 
-------------------------------------

### What were likely conflicts of interest? (WordCloud)


```{r}

renderPlot({
   data <- expB4D()
    conf <- data[,"Conflict"]
    if(length(conf)>0){
      d <- unlist(string.break.line(paste(conf,sep="\n")))
      d <- clean_vector(d)
      if(length(d)>0){
        corpus <- Corpus(VectorSource(d))
        corpus <- tm_map(corpus, removePunctuation)
        corpus <- tm_map(corpus, tolower)
        corpus <- tm_map(corpus, removeWords, stopwords("english"))
        corpus <- tm_map(corpus, stemDocument)
        corpus <- tm_map(corpus, PlainTextDocument)
        wordcloud(corpus, max.words=100, random.order=F)
      }  
    }
})
```




### What were likely conflicts of interest?? (Responses)


```{r}

library(Hmisc)

renderTable({
 data <- expB4D()
 conf <- data[,"Conflict"]
 if(length(conf)>0){
  resp <- unlist(string.break.line(conf))
 }else{
   resp <- c("")
 }
 resp <- clean_vector(resp)
 data.frame(Response=resp)
 
})


```

